Interval Probability for Fuzzy Quantum Theories

### 2016-07-14 prob.tex
discreteGBKS.bib @Article{BiglieriLops2007} Added...

The generalized Radon-Nikodym theorem is called Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA}
which states that, in Hilbert spaces of dimension $d\geq3$, given
a probability measure $\mu$, there exist a mixed state~$\rho$ that
induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
to the following corollary.

>>>>

The generalized Radon-Nikodym theorem is called Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007}
which states that, in Hilbert spaces of dimension $d\geq3$, given
a probability measure $\mu$, there exist a mixed state~$\rho$ that
induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
to the following corollary.
